### 2018-07-28 Sections/mathematical_representation_of_quantum_networks.tex
dB, \text->mathrm

To accommodate this, we allow the \textit{net cost} of a route to be defined as an arbitrary function of other primitive cost metrics and attributes of the route,
\begin{definition}[Net routing cost]\index{Net routing cost}
The net cost of a route \mbox{$A\to B$} is given by,
\begin{align} \label{eq:net_cost_R} \index{Net routing cost}
c_\text{net}(R) = f_\text{cost}(\vec{c}(R),\vec{a}(R)),
\end{align}
where $c_\text{net}$ is a single numeric value representing the net cost as calculated from an arbitrary cost function, $f_\text{cost}$, of the vector of associated costs and attributes.
\end{definition}
Note that the net routing cost needn't be a metric, as the cost function could be arbitrary. The net cost can be thought of as a ranking for routes, but not necessarily as a metric that accumulates across routes, since it already captures all these accumulations.

Eq.~(\ref{eq:net_cost_R}) gives us the net cost of a given route. For multiple users we would like to simultaneously optimise the cost across all users of the network. Thus we define the routing cost for the entire network to be,
\begin{definition}[Network routing cost]
	The net routing cost of all costs, over all active routes $\vec{R}$ is,
\begin{align} \label{eq:c_total}
c_\text{total}(\vec{R}_{\vec{A}\to \vec{B}}) = \sum_{r \in {\vec R}_{\vec{A}\to \vec{B}}} c_\text{net}(r),
\end{align}
where $\vec{R}_{\vec{A}\to \vec{B}}$ is a set of active routes connecting each pair \mbox{$A_i\to B_i~\forall ~ i$}.
\end{definition}

@@

Clearly the goal when choosing routing strategies is to minimise the total cost, Eq.~(\ref{eq:net_cost_R}). That is, solving the optimisation problem,
\begin{definition}[Strategy optimisation]
The optimisation of strategies with a network comprising net costs $c_\text{total}$ is given by,
\begin{align}
c_\text{min} &= \underset{\mathcal{S}}{\text{min}}(c_\text{total}), \nonumber \\
\mathcal{S}_\text{opt} &= \underset{\mathcal{S}}{\text{argmin}} (c_\text{total}).
\end{align}
\end{definition}

>>>>

To accommodate this, we allow the \textit{net cost} of a route to be defined as an arbitrary function of other primitive cost metrics and attributes of the route,
\begin{definition}[Net routing cost]\index{Net routing cost}
The net cost of a route \mbox{$A\to B$} is given by,
\begin{align} \label{eq:net_cost_R} \index{Net routing cost}
c_\mathrm{net}(R) = f_\mathrm{cost}(\vec{c}(R),\vec{a}(R)),
\end{align}
where $c_\mathrm{net}$ is a single numeric value representing the net cost as calculated from an arbitrary cost function, $f_\mathrm{cost}$, of the vector of associated costs and attributes.
\end{definition}
Note that the net routing cost needn't be a metric, as the cost function could be arbitrary. The net cost can be thought of as a ranking for routes, but not necessarily as a metric that accumulates across routes, since it already captures all these accumulations.

Eq.~(\ref{eq:net_cost_R}) gives us the net cost of a given route. For multiple users we would like to simultaneously optimise the cost across all users of the network. Thus we define the routing cost for the entire network to be,
\begin{definition}[Network routing cost]
	The net routing cost of all costs, over all active routes $\vec{R}$ is,
\begin{align} \label{eq:c_total}
c_\mathrm{total}(\vec{R}_{\vec{A}\to \vec{B}}) = \sum_{r \in {\vec R}_{\vec{A}\to \vec{B}}} c_\mathrm{net}(r),
\end{align}
where $\vec{R}_{\vec{A}\to \vec{B}}$ is a set of active routes connecting each pair \mbox{$A_i\to B_i~\forall ~ i$}.
\end{definition}

@@

Clearly the goal when choosing routing strategies is to minimise the total cost, Eq.~(\ref{eq:net_cost_R}). That is, solving the optimisation problem,
\begin{definition}[Strategy optimisation]
The optimisation of strategies with a network comprising net costs $c_\mathrm{total}$ is given by,
\begin{align}
c_\mathrm{min} &= \underset{\mathcal{S}}{\mathrm{min}}(c_\mathrm{total}), \nonumber \\
\mathcal{S}_\mathrm{opt} &= \underset{\mathcal{S}}{\mathrm{argmin}} (c_\mathrm{total}).
\end{align}
\end{definition}

### 2018-07-28 Sections/models_for_quantum_computation.tex
dB, \text->mathrm

Fig.~\ref{fig:eg_circuit} illustrates a simple 3-qubit quantum circuit comprising all of these elements. The interpretation of this diagram is as follows:
\begin{itemize}
	\item Horizontal lines represent individual qubits.
	\item Time flows from left to right (feedback is not allowed in the typical formalism for this representation).
	\item The three input qubits are labelled on the far-left as $\ket{\psi_1}$, $\ket{\psi_2}$ and $\ket{\psi_3}$.
	\item Single-qubit gates are denoted as boxes containing the name of the associated unitary operation. Here, the examples are the Hadamard ($\hat{H}$), Pauli bit-flip ($\hat{X}$), Pauli bit-phase-flip ($\hat{Y}$), and Pauli phase-flip ($\hat{Z}$) gates\index{Pauli operators}\index{Hadamard gate},
	\begin{align}
		\hat{H} &= \frac{1}{\sqrt{2}}\begin{pmatrix}
		1 & 1 \\
		1 & -1
		\end{pmatrix},\nonumber \\
		\hat{X} &= \begin{pmatrix}
		0 & 1 \\
		1 & 0
		\end{pmatrix},\nonumber \\
		\hat{Y} &= \begin{pmatrix}
		0 & -i \\
		i & 0
		\end{pmatrix},\nonumber \\
		\hat{Z} &= \begin{pmatrix}
		1 & 0 \\
		0 & -1
		\end{pmatrix}.
	\end{align}
	\item 2-qubit gates are denoted by vertical lines between the respective qubits.
	\item The maximally-entangling 2-qubit controlled-NOT (CNOT) gate\index{Controlled-NOT (CNOT) gate} is denoted via a control ($\bullet$) and a target ($\oplus$),
	\begin{align}
		\hat{\text{CNOT}}=\begin{pmatrix}
		1 & 0 & 0 & 0 \\
		0 & 1 & 0 & 0 \\
		0 & 0 & 0 & 1 \\
		0 & 0 & 1 & 0
		\end{pmatrix}.
	\end{align}
	This is the quantum equivalent of the classical XOR gate, flipping the target ($\hat{X}$) if the control is on.
	\item All quantum gates have the same number of input as output qubits. This is a necessary condition for the unitarity of quantum gates (\mbox{$\hat{U}^\dag \hat{U} = \hat{\mathbb{I}}$}).
	\item The maximally-entangling 2-qubit controlled-phase (CZ)\index{Controlled-Z (CZ) gate} gate is denoted by two targets ($\bullet$) (the gate operates symmetrically on its two qubits),
	\begin{align}
		\hat{\text{CZ}}=\begin{pmatrix}
		1 & 0 & 0 & 0 \\
		0 & 1 & 0 & 0 \\
		0 & 0 & 1 & 0 \\
		0 & 0 & 0 & -1
		\end{pmatrix},
	\end{align}
	applying a phase-gate ($\hat{Z}$) to the target if the control is on.
	\item The `meter' symbol represents a classical measurement in the Pauli $\hat{Z}$-basis (the computational or logical basis).
	\item Double lines represent classical feedforward of measurement outcomes, controlling a subsequent gate.
\end{itemize}

The circuit in Fig.~\ref{fig:eg_circuit} can be interpreted mathematically as implementing the following operation,
\begin{align}
	\ket\phi &= {\hat{Z}_3}^{m_1} \cdot {\hat{X}_3}^{m_2} \cdot \hat{M}_2 \cdot \hat{M}_1 \cdot \hat{Y}_1 \nonumber \\
	&\cdot \hat{\text{CZ}}_{1,2} \cdot \hat{\text{CNOT}}_{3,2} \cdot \hat{H}_3 \cdot \ket{\psi_1}\otimes\ket{\psi_2}\otimes\ket{\psi_3},
\end{align}
where $m_1$ and $m_2$ are the binary measurement outcomes of the two single-qubit $\hat{Z}$-basis measurements, $\hat{M}_1$ and $\hat{M}_2$.

@@

In the graph, vertices represent qubits initialised into the,
\begin{align}
	\ket{+}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1}),
\end{align}
state, and edges represent the application of maximally entangling CZ gates between vertices,
\begin{align}
	\ket\psi_\text{cluster} = \prod_{e\in E} \hat{\text{CZ}}_e \cdot \bigotimes_{v\in V}\ket{+}_v.
\end{align}
Alternately, but equivalently, cluster states may be defined in the stabiliser formalism\index{Stabiliser formalism}. Specifically, a cluster state is defined to be the joint +1 eigenstate of all the stabilisers,
\begin{align} \label{eq:CS_stab} \index{Cluster state stabilisers}
	\hat{S}_v = \hat{X}_v \prod_{i\in n_v} \hat{Z}_i,
\end{align}
where there is one stabiliser $\hat{S}_v$ per vertex $v$, and $n_v$ is the set of vertices neighbouring $v$. The cluster state therefore satisfies,
\begin{align}
	\hat{S}_v\ket\psi_\text{cluster} = \ket\psi_\text{cluster}\,\forall\, v,
\end{align}
and the full set of stabilisers, $\hat{S}_v$, over all vertices $v$ is sufficient to fully characterise the cluster state, $\ket{\psi}_\text{cluster}$, for a given graph topology.

@@

Mapping a circuit model computation to a cluster state topology can be most na{\" i}vely performed by taking a circuit acting on $n_\text{qubits}$ qubits with depth $n_\text{depth}$, preparing an \mbox{$n_\text{qubits}\times n_\text{depth}$} rectangular lattice cluster, and `etching' the circuit directly into the cluster state substrate. To perform this mapping we choose a universal gate set comprising CZ and single-qubit gates, retaining vertical edges where CZ gates ought to be present, eliminating the remaining vertical edges. Now we have a substrate that looks topologically very much like its equivalent circuit construction, and the computation proceeds chronologically in the same manner. The only conceptual distinction is that in the circuit model gates are directly applied chronologically to the set of qubits, whereas in the cluster state gate teleportation (Sec.~\ref{sec:teleport_gate}) is effectively implemented upon each measurement, with the action of gates accumulating as these teleportations are successively applied. A simple example of this notion is shown in Fig.~\ref{fig:cluster_state_circuit}.

@@

The second approach is to borrow techniques from percolation theory\index{Percolation theory} to simply tolerate defects in a cluster state lattice by working around them \cite{Brown}. Specifically, if the defect probability (i.e probability of a missing vertex or edge) is below some \textit{percolation threshold}\index{Percolation threshold}, \mbox{$p_\text{defect}\leq \epsilon_\text{threshold}$}, in the asymptotic limit we are guaranteed that routes exist through the lattice, enabling the required flow of information. This allows defective graphs to be employed for quantum computation.

>>>>

Fig.~\ref{fig:eg_circuit} illustrates a simple 3-qubit quantum circuit comprising all of these elements. The interpretation of this diagram is as follows:
\begin{itemize}
	\item Horizontal lines represent individual qubits.
	\item Time flows from left to right (feedback is not allowed in the typical formalism for this representation).
	\item The three input qubits are labelled on the far-left as $\ket{\psi_1}$, $\ket{\psi_2}$ and $\ket{\psi_3}$.
	\item Single-qubit gates are denoted as boxes containing the name of the associated unitary operation. Here, the examples are the Hadamard ($\hat{H}$), Pauli bit-flip ($\hat{X}$), Pauli bit-phase-flip ($\hat{Y}$), and Pauli phase-flip ($\hat{Z}$) gates\index{Pauli operators}\index{Hadamard gate},
	\begin{align}
		\hat{H} &= \frac{1}{\sqrt{2}}\begin{pmatrix}
		1 & 1 \\
		1 & -1
		\end{pmatrix},\nonumber \\
		\hat{X} &= \begin{pmatrix}
		0 & 1 \\
		1 & 0
		\end{pmatrix},\nonumber \\
		\hat{Y} &= \begin{pmatrix}
		0 & -i \\
		i & 0
		\end{pmatrix},\nonumber \\
		\hat{Z} &= \begin{pmatrix}
		1 & 0 \\
		0 & -1
		\end{pmatrix}.
	\end{align}
	\item 2-qubit gates are denoted by vertical lines between the respective qubits.
	\item The maximally-entangling 2-qubit controlled-NOT (CNOT) gate\index{Controlled-NOT (CNOT) gate} is denoted via a control ($\bullet$) and a target ($\oplus$),
	\begin{align}
		\hat{\mathrm{CNOT}}=\begin{pmatrix}
		1 & 0 & 0 & 0 \\
		0 & 1 & 0 & 0 \\
		0 & 0 & 0 & 1 \\
		0 & 0 & 1 & 0
		\end{pmatrix}.
	\end{align}
	This is the quantum equivalent of the classical XOR gate, flipping the target ($\hat{X}$) if the control is on.
	\item All quantum gates have the same number of input as output qubits. This is a necessary condition for the unitarity of quantum gates (\mbox{$\hat{U}^\dag \hat{U} = \hat{\mathbb{I}}$}).
	\item The maximally-entangling 2-qubit controlled-phase (CZ)\index{Controlled-Z (CZ) gate} gate is denoted by two targets ($\bullet$) (the gate operates symmetrically on its two qubits),
	\begin{align}
		\hat{\mathrm{CZ}}=\begin{pmatrix}
		1 & 0 & 0 & 0 \\
		0 & 1 & 0 & 0 \\
		0 & 0 & 1 & 0 \\
		0 & 0 & 0 & -1
		\end{pmatrix},
	\end{align}
	applying a phase-gate ($\hat{Z}$) to the target if the control is on.
	\item The `meter' symbol represents a classical measurement in the Pauli $\hat{Z}$-basis (the computational or logical basis).
	\item Double lines represent classical feedforward of measurement outcomes, controlling a subsequent gate.
\end{itemize}

The circuit in Fig.~\ref{fig:eg_circuit} can be interpreted mathematically as implementing the following operation,
\begin{align}
	\ket\phi &= {\hat{Z}_3}^{m_1} \cdot {\hat{X}_3}^{m_2} \cdot \hat{M}_2 \cdot \hat{M}_1 \cdot \hat{Y}_1 \nonumber \\
	&\cdot \hat{\mathrm{CZ}}_{1,2} \cdot \hat{\mathrm{CNOT}}_{3,2} \cdot \hat{H}_3 \cdot \ket{\psi_1}\otimes\ket{\psi_2}\otimes\ket{\psi_3},
\end{align}
where $m_1$ and $m_2$ are the binary measurement outcomes of the two single-qubit $\hat{Z}$-basis measurements, $\hat{M}_1$ and $\hat{M}_2$.

@@

In the graph, vertices represent qubits initialised into the,
\begin{align}
	\ket{+}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1}),
\end{align}
state, and edges represent the application of maximally entangling CZ gates between vertices,
\begin{align}
	\ket\psi_\mathrm{cluster} = \prod_{e\in E} \hat{\mathrm{CZ}}_e \cdot \bigotimes_{v\in V}\ket{+}_v.
\end{align}
Alternately, but equivalently, cluster states may be defined in the stabiliser formalism\index{Stabiliser formalism}. Specifically, a cluster state is defined to be the joint +1 eigenstate of all the stabilisers,
\begin{align} \label{eq:CS_stab} \index{Cluster state stabilisers}
	\hat{S}_v = \hat{X}_v \prod_{i\in n_v} \hat{Z}_i,
\end{align}
where there is one stabiliser $\hat{S}_v$ per vertex $v$, and $n_v$ is the set of vertices neighbouring $v$. The cluster state therefore satisfies,
\begin{align}
	\hat{S}_v\ket\psi_\mathrm{cluster} = \ket\psi_\mathrm{cluster}\,\forall\, v,
\end{align}
and the full set of stabilisers, $\hat{S}_v$, over all vertices $v$ is sufficient to fully characterise the cluster state, $\ket{\psi}_\mathrm{cluster}$, for a given graph topology.

@@

Mapping a circuit model computation to a cluster state topology can be most na{\" i}vely performed by taking a circuit acting on $n_\mathrm{qubits}$ qubits with depth $n_\mathrm{depth}$, preparing an \mbox{$n_\mathrm{qubits}\times n_\mathrm{depth}$} rectangular lattice cluster, and `etching' the circuit directly into the cluster state substrate. To perform this mapping we choose a universal gate set comprising CZ and single-qubit gates, retaining vertical edges where CZ gates ought to be present, eliminating the remaining vertical edges. Now we have a substrate that looks topologically very much like its equivalent circuit construction, and the computation proceeds chronologically in the same manner. The only conceptual distinction is that in the circuit model gates are directly applied chronologically to the set of qubits, whereas in the cluster state gate teleportation (Sec.~\ref{sec:teleport_gate}) is effectively implemented upon each measurement, with the action of gates accumulating as these teleportations are successively applied. A simple example of this notion is shown in Fig.~\ref{fig:cluster_state_circuit}.

@@

The second approach is to borrow techniques from percolation theory\index{Percolation theory} to simply tolerate defects in a cluster state lattice by working around them \cite{Brown}. Specifically, if the defect probability (i.e probability of a missing vertex or edge) is below some \textit{percolation threshold}\index{Percolation threshold}, \mbox{$p_\mathrm{defect}\leq \epsilon_\mathrm{threshold}$}, in the asymptotic limit we are guaranteed that routes exist through the lattice, enabling the required flow of information. This allows defective graphs to be employed for quantum computation.

### 2018-07-28 Sections/network_algorithms.tex
Figure reformatting to make double column, rather than stacked
mdframed
dB, \text->mathrm

\renewcommand{\tablename}{TABLE}

\begin{table*}[!htb]
	\begin{tabular}{|c|c|c|c|}
		\hline
  		\rowcolor{Dandelion} Algorithm & Description & Complexity class & Scaling \\
  		\hline
  		\hline
  		\rowcolor{LimeGreen} Breadth-first-search & Explore all vertices in a graph & \textbf{P} & $O(|V|+|E|)$ \\
  		\hline
  		\rowcolor{LimeGreen} Depth-first-search & (same as above) & \textbf{P} & $O(|V|+|E|)$ \\
		\hline
  		\rowcolor{LimeGreen} Shortest-path (Dijkstra) & Find the shortest route between two nodes & \textbf{P} & $O(|V|^2)$ \\
  		\rowcolor{LimeGreen} & in a directed graph & &  \\
  		  		\hline
		\rowcolor{LimeGreen} Shortest-path (\textit{A*}) & (same as above) & \textbf{P} & (varying) \\
  		  		\hline
		\rowcolor{LimeGreen} Single-source shortest path & Find the shortest paths from a given node to & \textbf{P} & $O(|V|\cdot |E|)$\\
  		\rowcolor{LimeGreen} & \textit{all} other nodes & & \\
 		\hline
		\rowcolor{LimeGreen} Minimum spanning tree & Find a spanning tree of a graph that minimises & \textbf{P} & $O(|E|\text{log}|V|)$ \\
  		\rowcolor{LimeGreen} & the total of the edge weights & & \\
  		\hline
  		\rowcolor{LimeGreen} Minimum cost flow & Minimise total costs in a network &  \textbf{P} & $O(|V|\text{log}|V|(|E|$\\
  		\rowcolor{LimeGreen} (Orlin) & with a specified amount of flow& & $+|V|\text{log}|V|))$ \\
  		\hline
  		\rowcolor{LimeGreen} Maximum flow & Maximise flow in a network, regardless of costs & \textbf{P} & $O(|E|\cdot c_\text{max})$ \\
  		\rowcolor{LimeGreen} (Ford-Fulkerson) & & & \\
  		\hline
  		\rowcolor{Lavender} Multi-commodity flow & Same as maximum flow, but generalised to & \textbf{NP}-complete & ? \\
  		\rowcolor{Lavender} & arbitrary numbers of users & (exactly), & \\
  		\rowcolor{Lavender} & & \textbf{P} (approximation & \\
  		\rowcolor{Lavender} & & using heuristics) & \\
  		\hline
  		\rowcolor{Lavender} Vehicle routing problem & Generalises the shortest-path algorithm to multiple & \textbf{NP}-complete & ? \\
  		\rowcolor{Lavender} & users, with distinct sources and destinations & & \\ 
  		\hline
  		\rowcolor{Lavender} Vehicle rescheduling problem & Same as above but with dynamically changing costs & \textbf{NP}-complete & ? \\
    	\hline
	\end{tabular}
	\caption{Summary of some important network algorithms and their complexities. The \textbf{NP}-complete algorithms are not believed to have efficient classical algorithms, and their exact scaling is not well understood.} \label{tab:net_alg_sum} \index{Network algorithms}\index{Breadth-first-search (BFS) algorithm}\index{Depth-first-search (DFS) algorithm}\index{Shortest-path algorithm}\index{Single-source shortest path algorithm}\index{Minimum spanning tree algorithm}\index{Minimum cost flow algorithm}\index{Maximum flow algorithm}\index{Multi-commodity flow algorithm}\index{Vehicle routing problem}\index{Vehicle rescheduling problem}
\end{table*}

\renewcommand{\tablename}{ALG.}

@@

Formally, let $\vec{R}$ be the set of all routes \mbox{$A\to B$}. Then,
\begin{align}
c_\text{opt} = \min_{r\in R} \left(\sum_{i\in r} c_\text{net}(i) \right),
\end{align}
where \mbox{$i\in r$} denotes the $i$th edge in the route $r$. Intuitively, the (in general) exponential number of possible paths through a graph might lead one to believe the above optimisation problem is a computationally inefficient one (such as \textbf{NP}-complete, or worse). However, perhaps surprisingly, Dijkstra's algorithm cleverly manages to reduce this to a polynomial-time problem. A sketch of the algorithm is provided in Alg.~\ref{alg:dijkstra}, which needn't be understood by the reader desperate to read further.

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function DijkstraShortestPath($G$,$A$,$B$):
\begin{enumerate}
	\item currentNode = $A$
    \item tentativeDistances[$A$] = 0
    \item tentativeDistances[others] = $\infty$
    \item nodesVisited[$A$] = True
    \item nodesVisited[others] = False
    \item loopStart:
    \item neighbours = currentNode.neighbourhood
    \item nodesVisited[neighbours] = True
    \item for(n$\in$neighbours) \{
    \setlength{\itemindent}{0.2in}
    \item newTentativeDist = \\ min(tentativeDistances[currentNode] \\+ edgeWeight[currentNode,n],\\
        tentativeDistances[n])\\
    \item nodesVisited[currentNode] = True
    \setlength{\itemindent}{0in}
    \item \}
    \item if(nodesVisited[$B$] = True) \{
    \setlength{\itemindent}{0.2in}
	\item return(tentativeDistances[$B$])
	\item $\Box$
    \setlength{\itemindent}{0in}
    \item \}
	\item currentNode = \\
	tentativeDistances[unvisitedNodes].\\
	nodeWithSmallest()
	\item goto(loop)
    \item $\Box$
\end{enumerate}}}}
\caption{Dijkstra's original shortest-path algorithm for finding the lowest weight path through a graph, $G$, between two vertices, $A$ (source) and $B$ (destination). The algorithm has $O(|V|^2)$ runtime (in \textbf{P}).} \label{alg:dijkstra}\index{Shortest-path algorithm}
\end{table}

Fig.~\ref{fig:simp_route_opt} illustrates a directed, edge-weighted graph. A shortest-path algorithm applied between vertices $A$ and $B$ would return \mbox{$R_\text{shortest} = A\to F\to B$} as the minimum cost route.

@@

One polynomial-time algorithm, by \cite{JAMES_B_ORLIN}, for solving this problem does so in, 
\begin{align}
	O(|V|\text{log}|V|(|E|+|V|\text{log}|V|)),
\end{align}
time.

@@

This problem can be tackled using a number of techniques. In some circumstances, linear programming techniques can be employed. The best-known algorithm is the Ford-Fulkerson algorithm\index{Maximum flow algorithm} \cite{???}, which finds a solution in,
\begin{align}
	O(|E|\cdot c_\text{max}),
\end{align}
runtime, where $|E|$ is the number of links in the network and $c_\text{max}$ is the maximum cost present in the network. The algorithm behaves pathologically in some conditions, which can easily be overcome in the context we present here. Using Ford-Fulkerson as a starting point, numerous other more sophisticated algorithms have been developed.

>>>>

\startnormtable
\begin{table*}[!htb]
	\begin{tabular}{|c|c|c|c|}
		\hline
  		\rowcolor{Dandelion} Algorithm & Description & Complexity class & Scaling \\
  		\hline
  		\hline
  		\rowcolor{LimeGreen} Breadth-first-search & Explore all vertices in a graph & \textbf{P} & $O(|V|+|E|)$ \\
  		\hline
  		\rowcolor{LimeGreen} Depth-first-search & (same as above) & \textbf{P} & $O(|V|+|E|)$ \\
		\hline
  		\rowcolor{LimeGreen} Shortest-path (Dijkstra) & Find the shortest route between two nodes & \textbf{P} & $O(|V|^2)$ \\
  		\rowcolor{LimeGreen} & in a directed graph & &  \\
  		  		\hline
		\rowcolor{LimeGreen} Shortest-path (\textit{A*}) & (same as above) & \textbf{P} & (varying) \\
  		  		\hline
		\rowcolor{LimeGreen} Single-source shortest path & Find the shortest paths from a given node to & \textbf{P} & $O(|V|\cdot |E|)$\\
  		\rowcolor{LimeGreen} & \textit{all} other nodes & & \\
 		\hline
		\rowcolor{LimeGreen} Minimum spanning tree & Find a spanning tree of a graph that minimises & \textbf{P} & $O(|E|\mathrm{log}|V|)$ \\
  		\rowcolor{LimeGreen} & the total of the edge weights & & \\
  		\hline
  		\rowcolor{LimeGreen} Minimum cost flow & Minimise total costs in a network &  \textbf{P} & $O(|V|\mathrm{log}|V|(|E|$\\
  		\rowcolor{LimeGreen} (Orlin) & with a specified amount of flow& & $+|V|\mathrm{log}|V|))$ \\
  		\hline
  		\rowcolor{LimeGreen} Maximum flow & Maximise flow in a network, regardless of costs & \textbf{P} & $O(|E|\cdot c_\mathrm{max})$ \\
  		\rowcolor{LimeGreen} (Ford-Fulkerson) & & & \\
  		\hline
  		\rowcolor{Lavender} Multi-commodity flow & Same as maximum flow, but generalised to & \textbf{NP}-complete & ? \\
  		\rowcolor{Lavender} & arbitrary numbers of users & (exactly), & \\
  		\rowcolor{Lavender} & & \textbf{P} (approximation & \\
  		\rowcolor{Lavender} & & using heuristics) & \\
  		\hline
  		\rowcolor{Lavender} Vehicle routing problem & Generalises the shortest-path algorithm to multiple & \textbf{NP}-complete & ? \\
  		\rowcolor{Lavender} & users, with distinct sources and destinations & & \\ 
  		\hline
  		\rowcolor{Lavender} Vehicle rescheduling problem & Same as above but with dynamically changing costs & \textbf{NP}-complete & ? \\
    	\hline
	\end{tabular}
	\caption{Summary of some important network algorithms and their complexities. The \textbf{NP}-complete algorithms are not believed to have efficient classical algorithms, and their exact scaling is not well understood.} \label{tab:net_alg_sum} \index{Network algorithms}\index{Breadth-first-search (BFS) algorithm}\index{Depth-first-search (DFS) algorithm}\index{Shortest-path algorithm}\index{Single-source shortest path algorithm}\index{Minimum spanning tree algorithm}\index{Minimum cost flow algorithm}\index{Maximum flow algorithm}\index{Multi-commodity flow algorithm}\index{Vehicle routing problem}\index{Vehicle rescheduling problem}
\end{table*}
\startalgtable

@@

Formally, let $\vec{R}$ be the set of all routes \mbox{$A\to B$}. Then,
\begin{align}
c_\mathrm{opt} = \min_{r\in R} \left(\sum_{i\in r} c_\mathrm{net}(i) \right),
\end{align}
where \mbox{$i\in r$} denotes the $i$th edge in the route $r$. Intuitively, the (in general) exponential number of possible paths through a graph might lead one to believe the above optimisation problem is a computationally inefficient one (such as \textbf{NP}-complete, or worse). However, perhaps surprisingly, Dijkstra's algorithm cleverly manages to reduce this to a polynomial-time problem. A sketch of the algorithm is provided in Alg.~\ref{alg:dijkstra}, which needn't be understood by the reader desperate to read further.

\begin{table}[!htb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function DijkstraShortestPath($G$,$A$,$B$):
\begin{enumerate}
	\item currentNode = $A$
    \item tentativeDistances[$A$] = 0
    \item tentativeDistances[others] = $\infty$
    \item nodesVisited[$A$] = True
    \item nodesVisited[others] = False
    \item loopStart:
    \item neighbours = currentNode.neighbourhood
    \item nodesVisited[neighbours] = True
    \item for(n$\in$neighbours) \{
    \setlength{\itemindent}{0.2in}
    \item newTentativeDist = \\ min(tentativeDistances[currentNode] \\+ edgeWeight[currentNode,n],\\
        tentativeDistances[n])\\
    \item nodesVisited[currentNode] = True
    \setlength{\itemindent}{0in}
    \item \}
    \item if(nodesVisited[$B$] = True) \{
    \setlength{\itemindent}{0.2in}
	\item return(tentativeDistances[$B$])
	\item $\Box$
    \setlength{\itemindent}{0in}
    \item \}
	\item currentNode = \\
	tentativeDistances[unvisitedNodes].\\
	nodeWithSmallest()
	\item goto(loop)
    \item $\Box$
\end{enumerate}}
\end{mdframed}
\caption{Dijkstra's original shortest-path algorithm for finding the lowest weight path through a graph, $G$, between two vertices, $A$ (source) and $B$ (destination). The algorithm has $O(|V|^2)$ runtime (in \textbf{P}).} \label{alg:dijkstra}\index{Shortest-path algorithm}
\end{table}

Fig.~\ref{fig:simp_route_opt} illustrates a directed, edge-weighted graph. A shortest-path algorithm applied between vertices $A$ and $B$ would return \mbox{$R_\mathrm{shortest} = A\to F\to B$} as the minimum cost route.

@@

One polynomial-time algorithm, by \cite{JAMES_B_ORLIN}, for solving this problem does so in, 
\begin{align}
	O(|V|\mathrm{log}|V|(|E|+|V|\mathrm{log}|V|)),
\end{align}
time.

@@

This problem can be tackled using a number of techniques. In some circumstances, linear programming techniques can be employed. The best-known algorithm is the Ford-Fulkerson algorithm\index{Maximum flow algorithm} \cite{???}, which finds a solution in,
\begin{align}
	O(|E|\cdot c_\mathrm{max}),
\end{align}
runtime, where $|E|$ is the number of links in the network and $c_\mathrm{max}$ is the maximum cost present in the network. The algorithm behaves pathologically in some conditions, which can easily be overcome in the context we present here. Using Ford-Fulkerson as a starting point, numerous other more sophisticated algorithms have been developed.

### 2018-07-28 Sections/network_topologies.tex
A little
dB, \text->mathrm

\section{Network topologies} \index{Network topologies}

@@

In the case of a balanced lattice, in which all edges are of equal weight, the cost of a route is the sum of the number of steps in the vertical and horizontal directions, also known as the Manhattan or $L_1$ distance,
\begin{align}
L_1 = |x_\text{start} - x_\text{finish}| + |y_\text{start} - y_\text{finish}|.
\end{align}
In this case, route finding is simplified, since \textit{all} routes, which strictly traverse in one direction vertically and one direction horizontally, are optimal and of equal distance.

@@

The \textit{depth} ($d$) of a tree is the maximum number of steps from the root node to a terminating node with no children. The depth scales between \mbox{$d=O(|V|)$}, for the trivial linear tree (\mbox{$b_i=1$}), and \mbox{$d=O(\text{log}|V|)$} for non-trivial branching parameters (i.e \mbox{$b_i\neq 1$}).

@@

A variation on the complete graph, $K_{|V|}$, is to instead have a randomised implementation of it, whereby each of the possible edges in $K_{|V|}$ occurs with probability \mbox{$0\leq p_\text{edge}\leq 1$}. We would thereby be able to tune between the complete graph and the completely disconnected graph, representing a randomly connected network with arbitrary average connectivity. Specifically, the average number of links emanating from any node is \mbox{$e_\text{av} = (|V|-1)p_\text{edge}$}. Note that random graphs might be disjoint, making them inappropriate for many networking applications. For asymptotically large random graphs, \textit{percolation theory} \cite{???} provides thresholds for $p_\text{edge}$ such that they remain connected \cite{???}. Fig.~\ref{fig:random_graph} illustrates several graphs with different edge connectivity probabilities.

\begin{figure*}[!htb]
\includegraphics[width=0.325\textwidth]{random_0}
\includegraphics[width=0.325\textwidth]{random_05}
\includegraphics[width=0.325\textwidth]{random_1}
\caption{The 15-vertex randomly-connected graph. This is the same as $K_{15}$ in Fig.~\ref{fig:complete_graph}, but where edges are present with probabilities \mbox{$p_\text{edge}=0,0.5,1$} (top to bottom).} \label{fig:random_graph}
\end{figure*}

>>>>

\section{Network topologies} \index{Network topologies}\label{sec:network_topologies}

@@

In the case of a balanced lattice, in which all edges are of equal weight, the cost of a route is the sum of the number of steps in the vertical and horizontal directions, also known as the Manhattan or $L_1$ distance,
\begin{align}
L_1 = |x_\mathrm{start} - x_\mathrm{finish}| + |y_\mathrm{start} - y_\mathrm{finish}|.
\end{align}
In this case, route finding is simplified, since \textit{all} routes, which strictly traverse in one direction vertically and one direction horizontally, are optimal and of equal distance.

@@

The \textit{depth} ($d$) of a tree is the maximum number of steps from the root node to a terminating node with no children. The depth scales between \mbox{$d=O(|V|)$}, for the trivial linear tree (\mbox{$b_i=1$}), and \mbox{$d=O(\mathrm{log}|V|)$} for non-trivial branching parameters (i.e \mbox{$b_i\neq 1$}).

@@

A variation on the complete graph, $K_{|V|}$, is to instead have a randomised implementation of it, whereby each of the possible edges in $K_{|V|}$ occurs with probability \mbox{$0\leq p_\mathrm{edge}\leq 1$}. We would thereby be able to tune between the complete graph and the completely disconnected graph, representing a randomly connected network with arbitrary average connectivity. Specifically, the average number of links emanating from any node is \mbox{$e_\mathrm{av} = (|V|-1)p_\mathrm{edge}$}. Note that random graphs might be disjoint, making them inappropriate for many networking applications. For asymptotically large random graphs, \textit{percolation theory} \cite{???} provides thresholds for $p_\mathrm{edge}$ such that they remain connected \cite{???}. Fig.~\ref{fig:random_graph} illustrates several graphs with different edge connectivity probabilities.

\begin{figure*}[!htb]
\includegraphics[width=0.325\textwidth]{random_0}
\includegraphics[width=0.325\textwidth]{random_05}
\includegraphics[width=0.325\textwidth]{random_1}
\caption{The 15-vertex randomly-connected graph. This is the same as $K_{15}$ in Fig.~\ref{fig:complete_graph}, but where edges are present with probabilities \mbox{$p_\mathrm{edge}=0,0.5,1$} (top to bottom).} \label{fig:random_graph}
\end{figure*}
